---
title: "Majors"
output: html_document
date: "2024-03-20"
---

#libraries
```{r}
library(ggplot2)
library(tidyverse)
library(plotly)
```
#read csv file
```{r}
data <-read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-10-16/recent-grads.csv")
```



# Box plot
```{r BOX PLOT}
data %>%
  ggplot(aes(x = reorder(Major_category, Median), y = Median)) +
  geom_boxplot() +
  coord_flip()
```

# Most earning major categories according to Median
```{r BAR GRAPH}
data %>%
  group_by(Major_category) %>%
  summarise(median = median(Median)) %>%
  arrange(desc(median)) %>%
  ggplot(aes(x = reorder(Major_category, median), y = median)) +
  geom_col() +
  coord_flip()
```

# what are the highest earning majors
```{r}
data %>% select(Major,Major_category,Median,P25th,P75th) %>% filter(Major_category>=100)%>% head(20) %>%  ggplot()+ geom_point(mapping = aes(reorder(Major,Median),Median,colour=Major_category))+ coord_flip()
```

# what are the lowest earning majors
```{r}
data %>%
  select(Major_category, Median, Major) %>% tail(20)%>%
  ggplot() +
  geom_point(mapping = aes(x = reorder(Major,-Median), y = Median))+coord_flip() 
```

# Most common majors categories-
```{r}
data %>%
  select(Major_category, Total) %>%
  group_by(Major_category) %>%
  summarise(Total = sum(Total, na.rm = TRUE)) %>%
  arrange(desc(Total)) %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Major_category, Total), y = Total,fill= Major_category)) +
  coord_flip()+ labs(x = "")+theme(legend.position = "none")
```



# What are the most common majors
```{r}
data %>% select(Major, Total) %>%group_by(Major) %>% summarise(Total = sum(Total, na.rm = TRUE)) %>% arrange(desc(Total)) %>% head(20)%>% ggplot()+ geom_col(mapping = aes(reorder(Major,Total),Total , fill = Major)) + coord_flip() + theme(legend.position="none")
```

# comparison of men and women , Major wise
```{r}
data %>%
  group_by(Major) %>%
  summarise(men = sum(Men),
            women = sum(Women),
            total = sum(men + women)) %>% arrange(desc(total)) %>% head(20) %>%
  gather(key = "gender", value = "count", men, women) %>%
  ggplot(aes(x = reorder(Major,count), y = count, fill = gender)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip()

```


# share of women major category wise
```{r}
by_majorcategory <- data %>%
  group_by(Major_category) %>%
  summarise(men = sum(Men, na.rm = TRUE),
            women = sum(Women, na.rm = TRUE),
            total = sum(Total, na.rm = TRUE),
            median_salary = sum(Sample_size * Median, na.rm=TRUE) / sum(Sample_size)) %>%
  mutate(tshare_women = women / total) %>%
  arrange(desc(tshare_women))

```

#median salaries vs share of women ,major category wise
```{r}
library(ggrepel)

by_majorcategory %>%
  ggplot(mapping = aes(x = tshare_women, y = median_salary)) +
  geom_point() +
  geom_text(mapping = aes( label = Major_category), nudge_x = 0.05, nudge_y = 0.05) + geom_smooth(method="lm")

```


#median salaries vs share of women ,major wise
```{r}
 G<-data %>% group_by(Major) %>% summarise(men=sum(Men),
                                      women= sum(ShareWomen),
                                      median=sum(Median),
                                      Major_category=Major_category,
                                      Sample_size=Sample_size,
                                      Major=Major) %>%mutate(Major_category=fct_lump(Major_category,4)) %>% arrange(desc(median)) %>% 
  ggplot(mapping = aes(x = women, y = median, colour= Major_category, size=Sample_size , label=Major))+geom_point() + geom_smooth(aes(group=1),method="lm") 

ggplotly(G)

```


#regression model of sharewomen on the salary
```{r}
data %>%
  group_by(Major) %>%
  select(Major, ShareWomen, Sample_size, Median) %>%
  as.data.frame() %>%
  lm(formula = Median ~ ShareWomen, weights = Sample_size) %>% summary()

```
